Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
sec framework intro

This section presents our second contribution, a framework for proving 
correctness of cast representations.
In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics (in the style of CEK machines) indexed by cast 
representations ($ C $). 
In subsection~\ref{secc:framework:correctness}, we prove when $ C $ is 
$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
\judgeSeval{C}{e}{o} $, that is, every $ surely\;\text{\lazyD} $ cast 
representation respects the semantics of \lazyD\ cast calculus. Having this 
theorem means when people want to prove a \lazyD\ cast reprentation is correct, 
all they have to do is to prove that their cast representation is $ surely \;
LazyD $ and apply our framework to this proof, which should be much simpler 
than proving equivalence of semantics.
We are working on a similar theorem for \lazyUD{}.

@@

\begin{definition}[Surely \lazyD\ Cast Representation]
	A cast representation is surely \lazyD\ if
	\begin{enumerate}
		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
		\item If $ \judgeType{v}{T_1} $,
		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
		then $ applyCast(seq(c_1,c_2),v) = 
		applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
		where 
		\[
		\begin{array}{rcl}
		\rOOsucc{v} >>= f & = & f(v) \\
		\rOOfail{l} >>= f & = & \rOOfail{l}
		\end{array}
		\]
		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
		\item If $ v : \star $, 
		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
		\item If $ v : P $,
		then $ applyCast(cast(\star,l,Q),\hcvOOinj{P}{v}) 
		= applyCast(cast(P,l,Q),v) $
		\item If $ v : P $,
		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
		\item If $ v : \POOunit $,
		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
		\item
		$ 
		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
		= 
		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$

>>>>

This section presents our second contribution, a framework for proving 
correctness of cast representations. The framework is a theorem saying that for 
all cast representation $ C $, if $ C $ satisfies a collection of properties, 
that an interpreter using $ C $ as the cast representation is extensionally 
equivalent to the standard interpreter for \lazyD\ cast calculus. 
We are working on a similar theorem for \lazyUD{}.

Firstly, let us define what we mean by \emph{cast representations}. The first 
three operators allow the interpreter to construct casts. We call them cast 
constructors. 
And the forth and last operator enable the interpreter to use casts.

To use the framework, users needs to prove that their cast representation is 
\emph{surely LazyD}. The properties of surely \lazyD\ allow the framework to 
compute the result of $ applyCast(c,v) $ without referring to its actual 
definitions. This is because every casts at runtime is constructed by one of 
the three cast constructors. The first property handles casts constructed by $ 
id(T) $. And the second property handles $ seq(c,c) $. All remaining properties 
handles $ cast(T,l,T) $. They are effectively a duplication of the $ 
applyCast(c,v) $ in \ineffCEKD\ (Fig.~\ref{fig:applyCast-D-C}).

\begin{definition}[Surely \lazyD\ Cast Representation]
	A cast representation is surely \lazyD\ if
	\begin{enumerate}
		\item If $ v : T $, then $ applyCast(id(T), v) = \mathtt{succ} \; v $
		\item If $ \judgeType{v}{T_1} $,
		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
		then $ applyCast(seq(c_1,c_2),v) = 
		applyCast(c_1,v) >>= \lambda v.applyCast(c_2,v) $ \\
		where 
		\[
		\begin{array}{rcl}
		\rOOsucc{v} >>= f & = & f(v) \\
		\rOOfail{l} >>= f & = & \rOOfail{l}
		\end{array}
		\]
		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
		then $ applyCast(cast(T_1, l, T_2),v) = \rOOfail{l} $
		\item If $ v : \star $, 
		then $ applyCast(cast(\TOOdyn,l,\TOOdyn),v) = \rOOsucc{v} $
		\item If $ v : P_1 $,
		then $ applyCast(cast(\star,l,P_2),\hcvOOinj{P_1}{v}) 
		= applyCast(cast(P_1,l,P_2),v) $
		\item If $ v : P $,
		then $ applyCast(cast(P,l,\star),v) = \rOOsucc{(\hcvOOinj{P}{v})} $
		\item If $ v : \POOunit $,
		then $ applyCast(cast(\POOunit,l,\POOunit),v) = \rOOsucc{v} $
		\item
		$ 
		applyCast(cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4}) ,
		\hcvOOfun{c_1}{\rho}{x}{b}{c_2}) \\
		= 
		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$

In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics (in the style of CEK machines) indexed by cast 
representations ($ C $). 
In subsection~\ref{secc:framework:correctness}, we prove when $ C $ is 
$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
\judgeSeval{C}{e}{o} $, that is, every $ surely\;\text{\lazyD} $ cast 
representation respects the semantics of \lazyD\ cast calculus. Having this 
theorem means when people want to prove a \lazyD\ cast reprentation is correct, 
all they have to do is to prove that their cast representation is $ surely \;
LazyD $ and apply our framework to this proof, which should be much simpler 
than proving equivalence of semantics.

@@
